Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-02 draft/draft.tex
progress

@@

\section{
Data
\label{sec:data}
}

The data comprehends 5 soccer leagues from England, France, Germany, Italy and Spain.
Each has 20 teams, with the exception of Germany which has 18.
For each pair of teams $i$ and $j$ of a given league, a score $\phi_{ij}\in \RR$ is provided, which is the aggregate of the two games between them, one as a local and another as a visitor.
There are ten different types of scores:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:}
\end{enumerate}

>>>>

See~\cite{perotti2025analysis,chacoma2025data}.

@@

\section{
Methods
\label{sec:methods}
}

\subsection{
Data
\label{sec:data}
}

The dataset covers five soccer leagues: England, France, Germany, Italy, and Spain.
Each league consists of 20 teams, except for Germany, which has 18.
Every pair of teams $i,j$ plays two matches: one with $i$ as the home team and $j$ as the away team, and the other with the reverse condition.
The teams are indexed according to their position in that year’s final standings.
For each pair of teams $i$ and $j$ in a given league, a metric $m_{ij}\in \mathbb{R}$ is provided, which takes a positive value if it presumably favors team $i$ over team $j$, and a negative value otherwise.
Different types of empirically determined metrics are considered:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:} bla bla,
\end{enumerate}
and metric-styles are also considered~\cite{chacoma2025data}.
Additionally, in order to test the inference of ratings, two types of ground truth metrics are also defined $m_{ij}=\frac{1}{2}(i-j)$ and $m_{ij}=\frac{1}{2}(\sigma_j-\sigma_i)$ using the rankings $i$ and scores $\sigma_i$ at the end of the season.
Note, $i<j$ if $\sigma_i>\sigma_j$ by definition.

{\color{red}[HERE...]}
